On The Benefits of Magnitude Estimation Relevance Assessments for Information Retrieval Evaluation

### 2016-09-16 response.tex

\documentclass[a4paper]{article}
\usepackage{xcolor}
\usepackage[top=20mm, bottom=20mm, left=20mm, right=20mm]{geometry}

@@

\newcommand{\comment}[1]{\vspace{1em} \textcolor{red}{{#1}} \vspace{1em}}

\begin{document}

We thank the reviewers for their constructive feedback and suggestions
for improvements.
Our responses to particular comments are outlined below.
Changes in the manuscript have been highlighted in red font to make
them easy to spot.

@@

\section{Reviewer 1}

In the footer on the first page, please add a concise statement of
the paper's addition after ``This paper is a revised and extended
version of [Turpin et al. 2015]; it adds XXX." By the way, you
should use [Author year] when you refer to a publication and Author
[year] when you refer to the author (citep{xxx} and citet{xxx},
respectively).

\comment{The citation style has been fixed, thank you. A detailed list of changes has
been added at the end of the related work section, in line with the next
item.}

@@

\comment {Thanks for pointing this out, we have added a paragraph in Section 2.3.}

Section 4: This is a better way of organizing the material than in
the SIGIR version. Collect and report on the data first. And only
interpret and conclude later. Moving bits from section 3 here (on
crowd judging and score normalization) makes good sense. Figures 1
and 2 are new. And so is section 4.2; adding a sentence to 4.2 with
the upshot of the section would be useful. The expansion of 4.3
(formerly 3.3) is useful.

\comment {We have added the sentence at the end of 4.2}

The new section 5 coincides more  or less with section 4 in the
SIGIR paper. Is ``We therefore next investigate judge agreement"
still a useful  way of ending this section, given the inclusion of
a new research question?

@@

\comment {Again, this seems fine on our copies.}

It would be good to explain the differences in absolute
numbers between Table IV in the TOIS submission and Table 2 in the
SIGIR paper. And why these differences do not matter.

\comment {We have added two sentences at the end of the first paragraph in Section~7.2 
explaining the difference. On closer inspection, we also noticed that the new methodology did make a
difference, and have altered the text in the final two paragraphs of Section~7.3 accordingly.}

Section 8: I am not sure I am happy with the uncertain ending of
this section. What does the disagreement with Kanoulas and Aslam's
earlier work mean for our ``ideal" evaluation setup?

\comment{We have added Section~8.1 Summary to clarify this.}

Section 9: the addition of a ``limitations" section is an excellent
idea.

@@

Appendix A: I like this addition. A screen dump of the instruction
interface would have been helpful.

\comment{The exact instructions that appeared on the screen are already
given in the appendix, and a screen dump would just format them in an
HTML/www style, rather than text.
As such, we don't think that an extra screen dump of the instructions
would be informative.
(In any case, it unfortunately turns out that CrowdFlower has undergone
an `upgrade' since we ran the experiments, so, sadly, the exact screen
shot is no longer available anyway.)
}

\end{document}

### 2016-09-16 2_bg.tex
Updates

\textcolor{red}{
This paper is based on a preliminary version published at 
SIGIR 2015~\cite{ME-SIGIR15}, but adds: RQ2; 
related background on crowdsourcing;
more information on the score distributions in Section~\ref{sec:descr-stat}, including
Figures~\ref{fig:ME-raw-scores} and~\ref{fig:ME-norm-scores} and their discussion;
a new Section~\ref{sec:cs} including Figure~\ref{fig:judgeVariability} and 
recomputation of Figure~\ref{fig:workersQuality};
new material in Section~\ref{sec:rq2}, including recomputation of 
Figures~\ref{fig:runs-rerank-median3best} and~\ref{fig:runs-rerank-median3best-fake}; 
a revised second half of Section~\ref{sec-rq3}; 
an Appendix giving exact participant instructions; and
additional references.
}

@@

>>>>

\textcolor{red}{ This paper is a revised and extended version of
research that appeared at SIGIR 2015~\cite{ME-SIGIR15}.
In particular, this version adds: a new research question of whether
crowdsourcing is a viable method to gather robust magnitude estimation
values (RQ2); related background on crowdsourcing; more information on
the ME score distributions reported in Section~\ref{sec:descr-stat},
including Figures~\ref{fig:ME-raw-scores} and~\ref{fig:ME-norm-scores}
and their discussion; a new Section~\ref{sec:cs} including
Figure~\ref{fig:judgeVariability} and recomputation of
Figure~\ref{fig:workersQuality}; new material in Section~\ref{sec:rq2},
including recomputation of Figures~\ref{fig:runs-rerank-median3best}
and~\ref{fig:runs-rerank-median3best-fake}; a revised second half of
Section~\ref{sec-rq3}; an Appendix giving exact participant
instructions; and additional references.
}

@@

\textcolor{red}{However, it is important to note that disagreement does
not necessarily imply low worker quality.
As pointed out for example by \citet{aroyo2015truth}, disagreement
might depend on the false assumption of a ``unique truth'', it might
carry useful information that can be exploited, and attempts to
eliminate disagreement, for example by detailed instructions, might not
improve quality and simply lead to information loss.}

### 2016-09-16 4_descriptive_stats.tex
Updates

\textcolor{red}{
Given that the  scores for document relevance that we have observed are 
distributed as seen previously in other tasks where magnitude estimation has been used, 
we can adopt normalizing and aggregating approaches that have been used before in
the literature.
}

>>>>

\textcolor{red}{ Given that the scores for document relevance that we
have observed are distributed similarly to other tasks where magnitude
estimation has been used, we can proceed to adopt normalizing and
aggregating approaches that have been used previously in the literature, as
explained in the next section.
}

### 2016-09-16 6_results_RQ2.tex
Updates

In our data, there are
at least ten workers judging the same topic-document pair, and
the source of internal disagreement might be threefold:
(i) the arbitrary, personal scale used by a judge when expressing an ME
score; 
(ii) the subjective nature of relevance; and 
(iii) the often-feared low quality of work in crowdsourcing exercises.
The first has already been discussed and is removed by the geometric
average normalization process (Section~\ref{sec:score-normalization}).
The second is a feature that one might not want to remove from the
data: different judges can truly have different opinions on the
relevance of a document, whatever scale of measurement is used.
Usually IR evaluators assume that this variation is distilled into a single 
value (for example: mean, median or mode) 
that represents a population of users \sm{, but there might not be a unique truth~\citep{aroyo2015truth}}.
Of course, the third source is in need of particular attention: low
quality workers might express unreliable scores, and in general this
would lead to low internal agreement.

@@

\sm{This argument is far from being conclusive but it confirms that
  the ten workers that we used in our experiment, and the associated
  cost, can be reduced. 
  Therefore, from the about $\$0.4$ for each document figure mentioned
  in Section~\ref{sec:crowd-judging} we can estimate that only about
  $\$0.3$  for each document are really needed, if not less since more
  efficient methods could be devised.}

>>>>

In our data, there are
at least ten workers judging the same topic-document pair, and
the source of internal disagreement might be threefold:
(i) the arbitrary, personal scale used by a judge when expressing an ME
score; 
(ii) the subjective nature of relevance; and 
(iii) the often-feared low quality of work in crowdsourcing exercises.
The first has already been discussed and is removed by the geometric
average normalization process (Section~\ref{sec:score-normalization}).
The second is a feature that one might not want to remove from the
data: different judges can truly have different opinions on the
relevance of a document, whatever scale of measurement is used.
Usually IR evaluators assume that this variation is distilled into a single 
value (for example: mean, median or mode) 
that represents a population of users \textcolor{red}{(although there might in fact not be a unique truth~\citep{aroyo2015truth})}.
Of course, the third source is in need of particular attention: low
quality workers might express unreliable scores, and in general this
would lead to low internal agreement.

@@

\textcolor{red}{While this argument is far from being conclusive, it
confirms that the ten workers that we used in our experiment, and the
associated cost, can be reduced.
Therefore, from the about $\$0.4$ for each document figure mentioned in
Section~\ref{sec:crowd-judging} we can estimate that only about $\$0.3$
for each document are really needed, if not less since more efficient
methods could be devised.}

### 2016-09-16 7_results_RQ3.tex
Updates

\textcolor{green}{
Generally the correlations between the system rankings based on 
categorical and ME gain values are higher when the wide judgements
are used as opposed to the narrow judgements.
This contradicts our expectations from 
Table~\ref{tab:scaling-cats}, which indicated that
a larger scale of gains led to a decrease in correlations.
This confirms that a simple argument based on the scale 
of judgements is not sufficient in explaining different system orders, 
although the number of topics used here is small (12).
We examine this further in the next section.
}

@@

\textcolor{red}{
In answering RQ\ref{item:rq2}, we have shown that there are clear
differences in system rankings using nDCG and ERR metrics on this data
when using ME scores as gain values compared with using ordinal
categories as gain values.
Depending on the judgements and the metric used, correlations between
system orderings using ME and the categorical judgements, as measured
with Kendall's $\tau$, varied between about 0.8 and -0.2. 
At first this might seem like a simple scaling problem, where 
ME judgements are over a wider range than categorical judgments.
While this is true, a much more likely explanation is that there is
substantial individual variance in not only how people perceive the
relevance of an individual document, but also in how they perceive the
ratio of relevance of one document to another.
}

>>>>

\textcolor{red}{
Generally the correlations between the system rankings based on 
categorical and ME gain values are higher when the wide judgements
are used as opposed to the narrow judgements.
This contradicts our expectations from 
Table~\ref{tab:scaling-cats}, which indicated that
a larger scale of gains led to a decrease in correlations.
This confirms that a simple argument based on the scale 
of judgements is not sufficient in explaining different system orders, 
although the number of topics used here is small (12).
We examine this further in the next section.
}

@@

\textcolor{red}{ In answering RQ\ref{item:rq2}, we have shown that
there are clear differences in system rankings using nDCG and ERR
metrics on this data when using ME scores as gain values compared with
using ordinal categories as gain values.
Depending on the judgements and the metric used, correlations between
system orderings using ME and the categorical judgements, as measured
with Kendall's $\tau$, varied between about 0.8 and -0.2. At first this
might seem like a simple scaling problem, where ME judgements are over
a wider range than categorical judgments.
However, analysis shows that simple factor cannot be the whole answer;
a much more likely explanation is that there is substantial individual
variance in not only how people perceive the relevance of an individual
document, but also in how they perceive the ratio of relevance of one
document to another.
}

### 2016-09-16 8_results_RQ4.tex
Updates

\textcolor{red}{
In the previous section, and in this section, we have seen not only 
that relevance values for a single document vary amongst users, but
the ratio of relevance between two documents also varies.
Thus, in answer to RQ\ref{item:rq3}, the selection of a single 
gain formulation as either
a linear or exponential mapping of categorical judgements
is guaranteed to misrepresent at least half of our users 
in this data set.
Similarly, choosing a single gain formulation to maximize statistical 
efficiency of system comparisons will also misrepresent a large 
part of the user population.
}

>>>>

\textcolor{red}{ In the previous section, and in this section, we have
seen not only that relevance values for a single document vary amongst
users, but the ratio of relevance between two documents also varies.
Thus, in answer to RQ\ref{item:rq3}, the selection of a single gain
formulation as either a linear or exponential mapping of categorical
judgements is guaranteed to misrepresent at least half of our users in
this data set.
Similarly, choosing a single gain formulation to maximize the
statistical efficiency of system comparisons will also misrepresent a
large part of the user population.
}
